A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-10-28 sections/appendix/descrete_event_simulation/main.tex
Add code archive (#14)
* Add repository archive to bibliography

* Cite archive

* Fix minor issue

* Recompile .pdf
Remove TODOs that were addressed
Minor changes on waiting zones
- Display waiting zones 1 and 2 on the queueing system
- Fix some text that listed the incorrect waiting zones

This model will be studied by using  
\lstinline[style=pystyle]{ambulance_game}.
Install the created library in your python environment, by running the 
following command in the command line:
\begin{lstlisting}[style=terminalstyle]
    $ python -m pip install ambulance_game
\end{lstlisting}

@@

in the command line or via the instructions provided in the GitHub repository.
% TODO: Cite repository

@@

Additional arguments that can be passed to the function are:
\begin{itemize}
    \item \textit{system\_capacity} (\(N\)): The maximum number of individuals in 
    waiting zone 2.
    \item \textit{buffer\_capacity} \(M\): The maximum number of individuals in 
    waiting zone 1.
    \item \textit{seed\_num}: The seed number for the random number generator.
    \item \textit{runtime}: How long to run the simulation for.
\end{itemize}

@@

\end{lstlisting}
% TODO: Fix code for proportion of individuals within time target

@@

% TODO: Archive simulation python code

>>>>

This model will be studied by using  
\lstinline[style=pystyle]{ambulance_game}~\cite{AmbulanceGame}.
Install the created library in your python environment, by running the 
following command in the command line:
\begin{lstlisting}[style=terminalstyle]
    $ python -m pip install ambulance_game
\end{lstlisting}

@@

in the command line or via the instructions provided in the GitHub repository.

@@

Additional arguments that can be passed to the function are:
\begin{itemize}
    \item \textit{system\_capacity} (\(N\)): The maximum number of individuals 
    in waiting zone 1.
    \item \textit{buffer\_capacity} \(M\): The maximum number of individuals in 
    waiting zone 2.
    \item \textit{seed\_num}: The seed number for the random number generator.
    \item \textit{runtime}: How long to run the simulation for.
\end{itemize}

@@

@@
